% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\input{packages}
\input{macros}

\newcommand{\lucas}[1]{\textcolor{pink}{Lucas: }\textcolor{blue}{#1} }
\newcommand{\phil}[1]{\textcolor{blue}{\textbf{Phil:} }\textcolor{blue}{#1} }

\begin{document}
%
\title{Atomic Swaps between Bitcoin and Monero}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Philipp Hoenisch\inst{1,2} \and
Lucas Soriano del Pino\inst{1,2}}
%
\authorrunning{Hoenisch et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{COMIT,
\email{\{firstname\}@comit.network} \and
CoBloX Pty Ltd, 
\email{\{firstname\}@coblox.tech}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% We see atomic swaps as necessary in a world with more than one blockchain.
% Not all blockchains are designed with interoperability in mind, but most depend on signature schemes which can be leveraged for this purpose.
% Monero is one such example and here we discuss the state of the art in Bitcoin-Monero atomic swaps and give a glimpse of what is to come.

Due to the evergrowing blockchain ecosystem, interoperability has become a matter of great importance. 
Atomic swaps allow connecting otherwise isolated blockchains while adhering to the core principles of censorship resistance and permissionlessnes. 
Up until recently, atomic swap protocols have mostly relied on complex script support, excluding certain types of blockchains.
With advances in cryptography, it is now possible to build a bridge between almost any two blockchains. 
In this work, we give an explanation of one such protocol which applies adaptor signatures on Bitcoin to procure atomic swaps between Monero and Bitcoin. 
We dive into the cryptographic details, discuss its limitations and give an outlook on our current work where we use adaptor signatures on the Monero signature scheme. 

\keywords{Blockchain  \and Atomic Swap \and Bitcoin \and Monero \and Adaptor Signatures.}
\end{abstract}
%
%
%
\input{introduction}

\input{htlc_atomic_swaps}

\input{old_protocol}

\input{new_protocol}

\input{conclusion}

%
% ---- Bibliography ----
%

\bibliographystyle{splncs04}
\bibliography{mybibliography}
\end{document}
